A quantitative framework for investigating the reliability of network construction

### 2018-06-07 manuscript/CI_interactions.tex
re-ordering is tough

    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

@@

    Beyond ``true" variation in network structure, several researchers have pointed to the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these preliminary efforts, to date we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling. Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web. We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

\section*{Why do some interactions \emph{not} occur?}

  To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed whether or not the interaction truly occurred. The detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.

    \subsection*{Interaction uncertainty}

      First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. If two species have incompatible traits, they may not interact even if there are no other constraints (e.g., temporal separation of species, inability to detect cryptic species) preventing the interaction from being observed. As a simple example, a prey species may be too large to be consumed by a particular predator. In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.

      Based on an observed network, however, it is often unclear whether an unobserved interaction is impossible due to incompatible traits or a rare phenomenon with $\lambda>0$. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016}. Nevertheless, every model is imperfect and lacks information (i.e. about traits) that could be used to define constraints on interactions~\citep{Dormann2017}. Some interaction uncertainty therefore remains in current trait-matching models. As more information about the influence of traits on interactions is uncovered, this uncertainty is likely to be reduced and $\lambda$ should either tend to 0 or to 1.

    \subsection*{Process uncertainty}

     Even when an interaction is feasible, i.e. $L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat. We define the local realisation of an interaction with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). In the field, however, process uncertainty is likely inevitable.

    \subsection*{Detection uncertainty}

      Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).

\section*{Estimating detection and process uncertainty}

@@

    The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur? How may we refine our sampling approaches to reduce uncertainties gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits). Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?

    The obvious rule of thumb is to ``sample more" (Fig.~\ref{upper_limits}). Sampling more will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}E-F). Thus, the more we sample, the more zeros will appear in our interaction matrix.

@@

    Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur. The bottom line is that separating different sources of uncertainty is difficult indeed. Nevertheless, we propose that information on the probability of detecting interactions in a focal system can be obtained by combining repeated sampling with prior information from the same or a similar system.

\section*{A naive quantification of uncertainty}

  We will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases. To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial. In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:

      \begin{equation}
        X \sim Bin(n,\lambda) ,
      \end{equation}

      \begin{equation}
         P(X = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
         \label{likelihood}
      \end{equation}

@@

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). Finding this estimate is therefore quite straightforward. Importantly, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X=0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples. % The non-point nature of lambda seems like a feature, not a bug.

  Treating $\lambda$ as a distribution does, however, have an important drawback. Where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement the data we have with other sources of information.

\section*{Bayesian approach to infer interaction probabilities}

    \subsection*{Posterior distribution of the interaction probability}

@@

    \subsection*{Moments and other properties}

@@

    \subsection*{The prior distribution}

@@

\section*{Scaling up to networks - an empirical example}

    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix} plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box 1 or \emph{Appendix S2} for a description). Using this dataset, we will demonstrate the derivation of prior distributions for the galler-natural enemy component of these networks (see \emph{Appendix S3} for the \emph{Salix}-galler component) and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}. Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.

@@

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
      (see \emph{Appendix S6} for details and code). Specifically, we obtained prior parameters of $\alpha$=0.700, $\beta$=8.49. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S7} for R implementation). For these interactions, we obtain $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).

      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact. Using the priors described above, our distribution would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}). The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}). The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S3}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S5}). The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

@@

\section*{Conclusions/recommendations}

@@

\begin{fullbox}{}
  \begin{spacing}{1.0}
    \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}C).
  \end{spacing}
\end{fullbox}

>>>>

    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

@@

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these preliminary efforts, we currently lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling. Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms} for an example). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we will first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. 
    % Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web and, finally, illustrate this framework using an extensively sampled empirical network.
    % We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

    \subsection*{Why do some interactions \emph{not} occur?}

      To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. The detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.

        \subsubsection*{Interaction uncertainty}

          First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. If two species have incompatible traits, they may not interact even if there are no other constraints (e.g., temporal separation of species, inability to detect cryptic species) preventing the interaction from being observed. As a simple example, a prey species may be too large to be consumed by a predator. In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.

          Based on an observed network, however, it is often unclear whether an unobserved interaction is impossible due to incompatible traits or simply a rare phenomenon with $\lambda>0$. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016}. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}. Some interaction uncertainty therefore remains in current trait-matching models. As more information about the influence of traits on interactions is uncovered, this uncertainty is likely to be reduced and $\lambda$ should either tend to 0 or to 1.

        \subsubsection*{Process uncertainty}

         Even when an interaction is feasible, i.e. $L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat. We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology describing the contingencies of interactions. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). In the field, however, process uncertainty is likely inevitable.

        \subsubsection*{Detection uncertainty}

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples of these difficulties and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).

    \subsection*{Estimating detection and process uncertainty}

@@

        The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur? How may we refine our sampling approaches to reduce uncertainties and gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits). Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?

        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more" (Fig.~\ref{upper_limits}). Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). Thus, the more we sample, the more zeros will appear in our interaction matrix.

@@

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur. The bottom line is that separating different sources of uncertainty is difficult indeed. Nevertheless, we propose that information on the probability of detecting interactions in a focal system can be obtained by combining repeated sampling with prior information from the same or a similar system. Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then illustrate this approach with an intensively and repeatedly sampled empirical dataset.

\section*{Materials and methods}

  \subsection*{A naive quantification of uncertainty}

    We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases. To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial. In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:

        \begin{equation}
          L \sim Bin(n,\lambda) ,
        \end{equation}

        \begin{equation}
           P(L = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
           \label{likelihood}
        \end{equation}

@@

    Note that $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

    To properly interpret $\lambda$, we need to estimate the variance as well as the MLE. The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$. It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). % The non-point nature of lambda seems like a feature, not a bug.

    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$. This means that where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement the data we have with other sources of information.

  \subsection*{Inferring interaction probabilities}

      \subsubsection*{Posterior distribution of the interaction probability}

@@

      \subsubsection*{Moments and other properties}

@@

      \subsubsection*{The prior distribution}

@@

\subsection*{Scaling up to networks - an empirical example}

    In the following section, we will provide an empirical example based on the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S2} for details).

    The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties. To do this, we first compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for the sake of brevity, present only the latter here. For the \emph{Salix}-galler component see \emph{Appendix S3}.

@@

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
      (see \emph{Appendix S5} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval" in \emph{Appendix S6}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S6}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S7}). The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

@@

\section*{Results}

  Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B). Moreover, even when a pair of species was observed to interact, the number of interactions was often lower than the number of co-occurrences (Fig.~\ref{histograms}C).

      We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49. Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}). When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}). The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S6}). The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).

\section*{Discussion}

  Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred. The number of observed co-occurrences strongly affected the posterior distribution of $\lambda$, meaning that our level of confidence that an interaction probability is below some threshold depends strongly on the amount of information available for each pair of species.

  [[Recap results]]

@@

% \begin{fullbox}{}
%   \begin{spacing}{1.0}
%     \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
%     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
%     \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}C).
%   \end{spacing}
% \end{fullbox}
